Fourmile Calibrations

### 2023-02-14 calibration_output.Rmd
updated relative map figs

@@

@@

@@

>>>>

Relative Tmean difference

```{r relative tmean, echo = F}

reg_tmean <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmean.csv',
                      skip = 13) %>%
  dplyr::select(-starts_with('@')) %>%
  mutate(time = dmy(time)) %>%
  summarize(across(`3`:`19`, ~ mean(.))) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmean_avg') %>%
  mutate(value = as.numeric(value))

hrus_map_tmean <- left_join(hrus_map_tmean, reg_tmean, by = 'value')

hrus_map_tmean <- hrus_map_tmean%>%
  mutate(relative_avgcum_diff = tmean_avg_cumdiff / tmean_avg)

tm_shape(hrus_map_tmean) +
  tm_polygons('relative_avgcum_diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

Relative Precip difference

```{r relative p, echo = F}

reg_p <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_precipAll.csv',
                      skip = 21) %>%
  dplyr::select(-starts_with('@')) %>%
  mutate(time = dmy(time)) %>%
  summarize(across(`3`:`19`, ~ mean(.))) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'precip_avg') %>%
  mutate(value = as.numeric(value))

hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value')

hrus_map_precip <- hrus_map_precip %>%
  mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg)

tm_shape(hrus_map_precip) +
  tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
tm_shape(locations_p) +
  tm_symbols(col='blue', size=4)

@@

Relative solar rad difference

```{r relative solrad, echo = F}

reg_solrad <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_solradAll.csv',
                      skip = 14) %>%
  dplyr::select(-starts_with('@')) %>%
  mutate(time = dmy(time)) %>%
  summarize(across(`3`:`19`, ~ mean(.))) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'solrad_avg') %>%
  mutate(value = as.numeric(value))

hrus_map_solrad <- left_join(hrus_map_solrad, reg_solrad, by = 'value')

hrus_map_solrad <- hrus_map_solrad %>%
  mutate(relative_avgcum_diff = solrad_avg_cumdiff / solrad_avg)

tm_shape(hrus_map_solrad) +
  tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
tm_shape(locations_solrad) +
  tm_symbols(col='blue', size=4)

@@

Relative RH difference

```{r relative rh, echo = F}

reg_rh <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_rhumAll.csv',
                      skip = 14) %>%
  dplyr::select(-starts_with('@')) %>%
  mutate(time = dmy(time)) %>%
  summarize(across(`3`:`19`, ~ mean(.))) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'rh_avg') %>%
  mutate(value = as.numeric(value))

hrus_map_rh <- left_join(hrus_map_rh, reg_rh, by = 'value')

hrus_map_rh <- hrus_map_rh %>%
  mutate(relative_avgcum_diff = rh_avg_cumdiff / rh_avg)

tm_shape(hrus_map_rh) +
  tm_polygons('relative_avgcum_diff', midpoint = NA, id = 'value') +
tm_shape(locations_rh) +
  tm_symbols(col='blue', size=4)

## Cumulative soil sat difference

```{r soilsat, echo = F}

#get rid of a bunch of data
hru_grid_soilSat <- hru_grids %>%
  dplyr::select(c(time, ID, soilSat)) %>%
  rename(soilSat_grid = soilSat)

hru_statn_soilSat <- hru_statn %>%
  dplyr::select(c(time, ID, soilSat)) %>%
  rename(soilSat_statn = soilSat)

soilSat_hrus <- left_join(hru_grid_soilSat, hru_statn_soilSat, by = c('time', 'ID')) %>%
  mutate(diff = soilSat_statn - soilSat_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>% 
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(soilSat_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_soilSat <- left_join(hrus, soilSat_hrus, by = 'value')

tm_shape(hrus_map_soilSat) +
  tm_polygons('soilSat_avg_cumdiff', midpoint = NA, id = 'value')

## Cumulative ET

```{r et, echo = F}

#get rid of a bunch of data
hru_grid_ET <- hru_grids %>%
  dplyr::select(c(time, ID, actET)) %>%
  rename(ET_grid = actET)

hru_statn_ET <- hru_statn %>%
  dplyr::select(c(time, ID, actET)) %>%
  rename(ET_statn = actET)

ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('time', 'ID')) %>%
  mutate(diff = ET_statn - ET_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>% 
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(ET_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')

tm_shape(hrus_map_ET) +
  tm_polygons('ET_avg_cumdiff', midpoint = NA, id = 'value')
